From the function-sheaf dictionary to quasicharacters of $p$-adic tori

### 2015-07-22 dictionary.tex
Changed section titles.

\section{Character Sheaves on commutative group schemes} \label{sec:category}

@@

\section{The function-sheaf dictionary for smooth commutative group schemes}\label{sec:main}

@@

\section{Applications to quasicharacters of $p$-adic tori and Abelian varieties}\label{sec:applications}

>>>>

\section{Definitions and recollections} \label{sec:category}

@@

\section{Character sheaves for smooth commutative group schemes}\label{sec:main}

@@

\section{Quasicharacter sheaves for $p$-adic tori}\label{sec:applications}
